%-------------------------
% Resume in Latex
% Author : Abshar Mohammed Aslam
% License : MIT
%------------------------

%--- Packages and Functions ----

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
%\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}
\usepackage[english]{babel}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Set the margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

% Set the margins
\geometry{left=0.85cm, top=0.8cm, right=0.85cm, bottom=0.2cm}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{\vspace{-2pt}}
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProject}[2]{
\vspace{0.5mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \hspace{-3mm}{#1}: & \hfill{\footnotesize{ #2}} \vspace{-0.5mm}\\ 
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeLeadership}[3]{
  \item
      \textbf{#1}\\#2 \\
      \textit{\small#3}\\

}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%

\newcommand{\name}{Abshar Mohammed Aslam}
\newcommand{\course}{B.E. -Computer Science and Engineering}
\newcommand{\phone}{50 486 5197}
\newcommand{\emaila}{absharaslam2001@gmail.com}
\newcommand{\github}{abxhr}
\newcommand{\website}{https://example.com}
\newcommand{\linkedin}{absharaslam}



\begin{document}
\fontfamily{cmr}\selectfont


%----------HEADING-----------------
\begin{center}
    \LARGE{\textbf{\name}}
\end{center}
\vspace{-4mm}
\begin{center}
    \small{\href{https://github.com/\github}{\faGithub \hspace{0.2mm} github.com/\github} |  \href{https://www.linkedin.com/in/\linkedin/}{\faLinkedinSquare \hspace{0.2mm} linkedin.com/in/\linkedin} | \href{mailto:\emaila}{\faSend \hspace{0.2mm} \emaila} | \faPhone \hspace{0.2mm} +971 \phone }
\end{center}
\vspace{-3mm}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Birla Institute of Technology and Science}{Dubai, UAE}
      {Bachelor's of Engineering in Computer Science;  CGPA: 8.98}{Sep. 2019 -- Aug. 2023}
    \resumeSubheading
      {Gulf Asian English School}{Sharjah, UAE}
      {Higher Secondary Education;  Grade: 92\%}{Apr. 2007 -- Mar. 2019}
  \resumeSubHeadingListEnd


%-----------Work Experience-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ESRI}{Sharjah, UAE}
      {Incoming Software Engineer Intern}{Aug. 2022 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Automated development workflows of ArcGIS Image Dedicated (AID) using GitHub Actions.}
        \resumeItem{}
          {Integrated inspection standards to AWS EKS across various regions using Prometheus and Grafana.}
        \resumeItem{}
          {Developed the testing workflow for all the Imagery Services (REST APIs) within ArcGIS Image Dedicated.}
        \resumeItem{}
          {Optimized the Build processes within AWS CodeBuild using multi-threading.}
        \resumeItem{}
          {Fixed multiple security issues within ArcGIS Image Dedicated to improve code quality.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \vspace{2mm}
    \resumeSubheading
      {Emirates}{Dubai, UAE}
      {Revenue Optimization Intern}{Jun. 2021 - Aug. 2021}
      \resumeItemListStart
        \resumeItem{}
          {Developed a novel machine learning Clustering Model to analyze clusters of Emirates SkyCargo profiles.}
        \resumeItem{}
          {Built a web tool to facilitate the team to view the cluster profiles using Plotly.}
        \resumeItem{}
          {Integrated the Clustering Model with Azure to allow real-time data analysis of Cargo at Emirates.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Research Experience-----------------
%\section{Research Experience}


%-----------PROJECTS-----------------
\section{Projects}
\vspace{-0.4mm}

\resumeSubHeadingListStart

	\resumeProject{\textbf{Arabic Natural Language Processing and Sentiment Analysis}}
	{\raisebox{0.75pt}{Mar. 2022}}
    \vspace{-5.5mm}
      \resumeItemListStart
        \resumeItem{}
          {Developed an NLP Model to recognize the Arabic Language, including all its dialects from the Middle East Region.}
        \resumeItem{}
          {Scrapped Tweets of various Arabic Dialects to create a corpus to train the NLP Model.}
        \resumeItem{}
          {Designed a tool using the created NLP Model to analyze the sentiment of any prompt in Arabic.}
      \resumeItemListEnd
 
    \vspace{-15pt}
    
    \resumeProject{\textbf{Instance and Semantic Segmentation using Mask-RCNN and ArcGIS}}
	{\raisebox{0.75pt}{Nov. 2021}}
    \vspace{-5.5mm}
      \resumeItemListStart
        \resumeItem{}
          {Developed a model to find instance and semantic segments of roads, buildings, and swimming pools, from the data from the ArcGIS Platform (ArcGIS Python API).}
        \resumeItem{}
          {Created a front-end using Dash framework, to easily navigate through the map and find segments in real-time.}
        \resumeItem{}
          {Deployed the front-end using GitHub Actions CI/CD for a better workflow.}
      \resumeItemListEnd
      
    \vspace{-15pt}
    
    \resumeProject{\textbf{Game AI for Super Mario Bros}}
	{\raisebox{0.75pt}{Nov. 2021}}
    \vspace{-5.5mm}
      \resumeItemListStart
        \resumeItem{}
          {Developed a Game Playing AI using Deep Reinforcement Learning, to navigate through the map of the game “Super Mario Bros” and score the maximum possible.}
        \resumeItem{}
          {Included various Stochastic Functions to ensure smooth functioning of the Game AI.}
      \resumeItemListEnd
      
    \vspace{-15pt}
    
    \resumeProject{\textbf{\href{https://github.com/abxhr/Open-DSA}Open DSA}}
	{\raisebox{0.75pt}{Feb. 2021}}
    \vspace{-5.5mm}
      \resumeItemListStart
        \resumeItem{}
          {An open-source library containing the implementation of many essential Data Structures and Algorithms.}
        \resumeItem{}
          {Data structures include from basic Stacks and Queues to advanced Trees and Graphs.}
        \resumeItem{}
          {Algorithms such as various Sorting and Searching techniques and more.}
        \resumeItem{}
          {Each topic detailed from their time complexities to their applications.}
      \resumeItemListEnd
	

\resumeSubHeadingListEnd

\vspace{-17pt}


%-----------Technical Skills-----------------
\section{Technical Skills}
\vspace{0.2mm}

\small{
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
\hspace{10pt}Languages \ & Python, \hspace{2pt}C++, \hspace{2pt}C, \hspace{2pt}JavaScript, \hspace{2pt}Java\\
\vspace{2pt}
\hspace{10pt}DevOps & Docker, \hspace{2pt}Kubernetes, \hspace{2pt}Terraform, \hspace{2pt}Packer, \hspace{2pt}GitHub Actions\\
\vspace{2pt}
\hspace{10pt}AWS & S3, \hspace{2pt}EC2, \hspace{2pt}EKS, \hspace{2pt}CodeBuild, \hspace{2pt}DynamoDB, \hspace{2pt}SQS, \hspace{2pt}SES\\
\vspace{2pt}
\hspace{10pt}Databases & MySQL, \hspace{2pt}PostgreSQL, \hspace{2pt}MongoDB\\
\vspace{2pt}
\hspace{10pt}ML/AI & Tensorfow, \hspace{2pt}Scikit-learn, \hspace{2pt}Natural Language Tool Kit, \hspace{2pt}OpenCV \\
\vspace{2pt}
\hspace{10pt}Data Analytics & Pandas, \hspace{2pt}Numpy, \hspace{2pt}Matplotlib, \hspace{2pt}Plotly, \hspace{2pt}MySQL, \hspace{2pt}Beautiful Soup\\
\vspace{2pt}
\hspace{10pt}Web Technologies & HTML, \hspace{2pt}CSS, \hspace{2pt}Django, \hspace{2pt}Flutter\\
\vspace{2pt}
\hspace{10pt}Miscellaneous & Git, \hspace{2pt}Selenium, \hspace{2pt}Linux, \hspace{2pt}Bash, \hspace{2pt}PowerShell\\
\vspace{2pt}
\end{tabular}
}

\vspace{-2.5mm}

%-----------Relevant Coursework-----------------
\section{Relevant Coursework}

\vspace{1mm}

\small{
  {
  $\bullet$ Data Structures
  \hspace{2mm}
  $\bullet$ Design \& Analysis of Algorithms
  \hspace{2mm}
  $\bullet$ Operating Systems
  \hspace{2mm}
  $\bullet$ Compiler Construction 
  \hspace{2mm} \\
  \vspace{1mm}
  $\bullet$ Database Systems 
  \hspace{2mm}
  $\bullet$ Theory of Computation 
  \hspace{2mm}
  $\bullet$ Computer Networks 
  \hspace{2mm}
  $\bullet$ Artificial Intelligence 
  \hspace{2mm}
  $\bullet$ Deep Learning \\
  \vspace{1mm}
  $\bullet$ Data Mining 
  \hspace{2mm}
  $\bullet$ Object Oriented Programming
  \hspace{2mm}
  $\bullet$ Discrete Structures 
  \hspace{2mm}
  $\bullet$ Logic in Computer Science \\
  \vspace{1mm}
  $\bullet$ Computer Architecture 
  \hspace{2mm}
  $\bullet$ Principles of Programming Languages 
  \hspace{2mm}
  $\bullet$ Optimization}\\
}

\vspace{-1mm}

%-----------Achievements-----------------
\section{Achievements}

\vspace{1mm}

\small{

{$\bullet$ Finalists for \textit{GCC’s Eureka Startup Competition 2021}.}\\
\vspace{1mm}
{$\bullet$ Conducted an 8-week Coding Bootcamp (with support from \textit{GitHub}).}\\
\vspace{1mm}
{$\bullet$ Conducted a workshop on "Open-Source", in collaboration with \textit{IBM}, \textit{AWS}, \textit{Microsoft Reactor}, and \textit{AstroLabs Dubai}.}\\
\vspace{1mm}
{$\bullet$ Conducted a 6-week Machine Learning Bootcamp, with 500 AED+ sponsorship from \textit{GitHub}.}\\
\vspace{1mm}
{$\bullet$ First GitHub Campus Expert from the GCC Region.}\\
\vspace{1mm}
{$\bullet$ Among top 50 Coders in \textit{Skyline Coding Challenge}.}\\
\vspace{1mm}
{$\bullet$ Best Outgoing Student Award - \textit{Gulf Asian English School}}\\
\vspace{1mm}

}

\vspace{-2.5mm}


%-----------Leadership-----------------
\section{Leadership}

\vspace{-10pt}

\begin{multicols}{2}
	\begin{itemize}
		\resumeLeadership{President}{Aug. 2022 - Present}{Alumni Relations Division, BPDC}
		\resumeLeadership{Secretary}{Jun. 2021 – Present}{ACM BITS Pilani Dubai Campus}
		\resumeLeadership{Day Scholar Rep.}{Dec. 2020 - Present}{BITS Pilani Dubai Campus}
		\resumeLeadership{General Secretary}{Aug. 2021 - Aug. 2022}{Alumni Relations Division, BPDC}
		\resumeLeadership{Head Boy}{2018 - 2019}{Gulf Asian English School}
		\resumeLeadership{Asst. Head Boy}{2017 - 2018}{Gulf Asian English School}
	\end{itemize}
\end{multicols}

%-----------Community----------------
\section{Community}

\vspace{-10pt}
\begin{multicols}{2}
	\begin{itemize}
		\resumeLeadership{GitHub Campus Expert}{Jun. 2021 – Present}{GitHub}
		\resumeLeadership{Microsoft Learn Student Ambassador}{Oct. 2021 – Present}{Microsoft}
		\resumeLeadership{Student Champion}{Nov. 2020 – Present}{Expo 2020}
		\resumeLeadership{AngelHack Student Ambassador}{Jun. 2021 – Present}{AngelHack}
	\end{itemize}
\end{multicols}

%-----------Miscellaneous-----------------
\section{Miscellaneous}

\vspace{1mm}

\small{
	\textbf{Languages: }{English, Malayalam, Hindi, Arabic, Urdu}\\
  \vspace{1mm}
	\textbf{Blog: }{\href{https://abxhr-learning.vercel.app/}https://abxhr-learning.vercel.app/\\
  \vspace{1mm}
	\textbf{LinkedIn: }{\href{https://linkedin.com/in/absharaslam}https://linkedin.com/in/absharaslam\\
}

\end{document}